---
title: "Full Title"
shorttitle: "Short Title"
author: 
  - name: "Eric R. Scott"
    institute: 
      - UF_WEC
    email: "scottericr@gmail.com"
    correspondence: true
  - name: "Author Two"
    institute: 
      - UF_WEC
      - affiliation2
    email: "email@university.edu"
    correspondence: false
bibliography: references.bib
keywords: |
  keyword1; keyword2; keyword3
execute: 
  echo: false
  warning: false
  error: false
institute: 
  - UF_WEC: "Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430"
  - affiliation2: "Department of Ecology, Evolution and Environmental Biology, Example University 123 Center Avenue, New York, New York 10027 USA"
filters: 
  - build/scholarly-metadata.lua
  - build/author-info-blocks.lua
  - quarto
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following shortcodes you can access and display values from the yml header above. -->

Running title: {{< meta shorttitle >}}

Keywords: {{< meta keywords >}}

<!-- The actual document text starts here: -->

\pagebreak

# Abstract

Abstract text.

\pagebreak

# Introduction

Introduction with an in-text citation [@scottDelayedEffectsClimate2022].

A cross-referencable equation:

$$
y=mx+b
$$ {#eq-line}

# Methods

Methods text.

# Results

A reference to A reference to @tbl-iris.

A reference to @fig-plot.

A reference to @eq-line.

# Discussion

# Acknowledgments

We thank \_\_\_, \_\_\_, and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
Financial support was provided by the U.S.
National Science Foundation (awards \_\_\_\_, and \_\_\_\_).
The authors declare no conflicts of interest.

# Author CRediT Statement

<!-- https://casrai.org/credit/ -->

# Data Availability Statement

Data and R code used in this study are archived with Zenodo at <doi url>.

\pagebreak

# Tables

```{r}
library(pander)
```

```{r example-table, results='asis'}
pandoc.table(
  head(iris),
  justify = c("right", "right", "right", "right", "left"),
  full_width = FALSE,
  caption = "A table must include a #tbl- label in curly braces at the end of the caption in order to cross-reference it correctly. {#tbl-iris}"
)
```

# Figures

```{r}
#| label: fig-plot
#| fig-cap: "A figure caption.  It can be long and potentially span
#|  multiple lines in the code chunk like this one."

plot(cars)
```

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::
